%%%%%%% Run this file with XeLaTeX or LuaLaTeX: xelatex resume.tex %%%%%%%

\documentclass[11pt,a4paper]{article}

% --------------------
% Packages
% --------------------
\usepackage[margin=0.8cm,footskip=10pt]{geometry}
\usepackage{parskip}
\usepackage{setspace}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{soul} % underline that wraps properly

% --------------------
% Base formatting
% --------------------
\newlength{\cvH}
\setlength{\cvH}{\dimexpr\textheight-\topskip\relax}
\setstretch{1.05}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, itemsep=0.2em, topsep=0.2em}

% Underline tuning for soul: \setul{depth}{thickness}
\setul{0.30ex}{0.12ex}

% Font (XeLaTeX / LuaLaTeX required)
\setmainfont{Times New Roman}

% Colors
\definecolor{cvblue}{HTML}{517DB5}
\definecolor{cvgray}{HTML}{848282}
\colorlet{cvlinegray}{cvgray!55}

% Training item indent
\newlength{\trainindent}
\setlength{\trainindent}{1.2em} % adjust to taste


% Convenience commands
\newcommand{\bluebf}[1]{{\color{cvblue}\textbf{#1}}}
\newcommand{\graybf}[1]{{\color{cvgray}\textbf{#1}}}
\newcommand{\blackbf}[1]{{\color{black}\textbf{#1}}}

\newcommand{\gray}[1]{{\color{cvgray}#1}}
\newcommand{\blue}[1]{{\color{cvblue}#1}}
\newcommand{\black}[1]{{\color{black}#1}}

% Underlined links
\newcommand{\grayulink}[2]{%
  \href{#1}{\gray{\ul{#2}}}%
}

\newcommand{\blueulink}[2]{%
  \href{#1}{\blue{\ul{#2}}}%
}

\newcommand{\blackulink}[2]{%
  \href{#1}{\color{black}\ul{#2}}%
}

\newcommand{\yearhdr}[1]{%
  \vspace{0.25em}%
  {\black{#1}}\par
  \vspace{0.25em}%
}


% --------------------
% Left column helpers
% --------------------
\newcommand{\lrule}{%
  \vspace{0.6em}%
  \centerline{{\color{cvlinegray}\rule{0.5\linewidth}{0.5pt}}}%
  \vspace{0.6em}%
}

\newcommand{\lsectionblock}[2]{%
  \graybf{#1}\par
  \vspace{0.6em}%
  #2\par
  \lrule
}

% --------------------
% Right column helpers
% --------------------
\newcommand{\rheading}[1]{%
  \vspace{0.6em}%
  \noindent\makebox[\linewidth]{%
    \leaders\hrule height 0.5pt\hfill
    \hspace{2em}\graybf{#1}\hspace{2em}%
    \leaders\hrule height 0.5pt\hfill
  }%
  \vspace{0.6em}%
}

% --------------------
% Double vertical separator
% --------------------
\newcommand{\doublevsep}{%
  \begin{minipage}[t][\cvH][c]{0.03\textwidth}
    \centering
    \vspace{0pt}%
    {\color{cvlinegray}\rule{0.5pt}{\cvH}\hspace{1.6pt}\rule{0.5pt}{\cvH}}%
  \end{minipage}%
}

% --------------------
% Page macro: two columns + separator (unbreakable per page)
% Left + right vertically centered
% --------------------
\newcommand{\cvpage}[2]{%
  \noindent
  \begin{minipage}[t][\cvH][c]{0.30\textwidth}
    \centering
    \vspace{0pt}%
    #1
  \end{minipage}
  \hfill
  \doublevsep
  \hfill
  \begin{minipage}[t][\cvH][c]{0.64\textwidth}
    \vspace{0pt}%
    #2
  \end{minipage}
  \par\newpage
}

\newcommand{\trainitem}[2]{%
  \par\noindent
  \hangindent=\trainindent
  \hangafter=1
  {\gray{\textperiodcentered}}\hspace{0.5em}%
  \blue{#1}%
  \if\relax\detokenize{#2}\relax\else\hspace{0.6em}\gray{#2}\fi
  \par\vspace{0.18em}%
}


\begin{document}

% ============================================================
% PAGE 1
% ============================================================
\cvpage{

{\fontsize{42}{44}\selectfont Valentin Guigon}\par
\vspace{0.8em}

\lrule

\lsectionblock{CURRENT\\POSITION}{
\blue{Postdoctoral researcher}\par
\grayulink{https://sldlab.umd.edu/}{Social Learning and Decisions Lab}\par
\gray{UMD | March 2024 -- ongoing}\par
\vspace{0.6em}
\blue{Affiliate researcher}\par
\grayulink{https://aim.umd.edu/}{Artificial Intelligence Interdisciplinary Institute at Maryland}\par
\vspace{0.6em}
\grayulink{https://nacs.umd.edu/}{Neuroscience and Cognitive Science (NACS) program, UMD}\par
}

\lsectionblock{RESEARCH\\AND PERSONAL\\INTERESTS}{
\gray{Beliefs}\par
\gray{Emotions}\par
\gray{Information}\par
\gray{Social learning}\par
\gray{Decision-making}\par
\gray{Computational psychiatry}\par
\gray{Computational neuroscience}\par
\gray{NeuroAI}\par

\vspace{0.9em}

\gray{Social sciences}\par
\gray{Public policies}\par
\gray{Epistemology}
}

\lsectionblock{CONTACT}{
\gray{+33 6 68 74 10 64}\par
\gray{+1 202 627 8960}\par
\vspace{0.9em}
\gray{3150 Biology--Psychology Building}\par
\gray{4094 Campus Dr, College Park}\par
\gray{MD 20742, USA}\par
\vspace{0.9em}
\grayulink{mailto:vguigon@umd.edu}{vguigon@umd.edu}\par
\grayulink{https://valentinguigon.github.io/}{personal website}\par
\grayulink{https://github.com/ValentinGuigon}{github}
}



}{

\rheading{PHD THESIS}

\parbox{0.95\linewidth}{\centering
\blackbf{Guigon, V.}\black{(2022). }
\blackulink{https://theses.hal.science/tel-04817845}
{Neurocognitive mechanisms underlying transmission of uncertain information in humans.}\par
}
\vspace{0.7em}



\rheading{EDUCATION}

\bluebf{Doctorate degree -- Biology: Cognitive neuroscience}\par
\graybf{2018--2022 \,|\, Neurosciences and Cognition Doctorate School, Lyon 1, France}

\vspace{0.6em}

\bluebf{Master degree -- Cognitive science}\par
\graybf{2016--2018 \,|\, Psychology Faculty, Lyon 2, France}

\vspace{0.6em}

\bluebf{Licence degree -- Physiology \& Neuroscience (Cognitive and Adaptative)}\par
\graybf{2015--2016 \,|\, Sciences Faculty, Marseille Saint-Charles, France}

\vspace{0.6em}

\bluebf{Licence degree -- Psychology}\par
\graybf{2012--2015 \,|\, Human Sciences Faculty, Aix-en-Provence, France}

\vspace{1.0em}



\rheading{RESEARCH EXPERIENCE}

\bluebf{Post-doctorate | Social Learning and Decisions Lab}\par
Department of Psychology, University of Maryland, MD, USA\par
March 2024 -- ongoing \,|\, Social decision making

\gray{Studies: Neurocomputational mechanisms underlying neurotypical and neuroatypical learning in social contexts. Individual differences in dynamic belief updating during trust learning.}\par
\gray{Tools: Matlab (SPM), R, Python (PyMC, fMRIprep, Nilearn, Fitlins)}\par
\gray{Project management: Behavioral and neuroimaging studies, Lab Operations, Lab Automatization}\par
\gray{Management: Joshua Berman, Atharv Umap, Gaurav D. Mahajan}\par
\gray{PI: Caroline Charpentier}

\vspace{0.9em}

\bluebf{Post-doctorate | Neuroeconomics (ISCMJ \& GATE)}\par
CNRS UMR 5229 \& CNRS UMR 2824, France\par
March 2023 -- October 2023 \,|\, Social decision making

\gray{Studies: Neurocognitive mechanisms underlying transmission of uncertain information in humans. Beliefs updating in social networks.}\par
\gray{Tools: Matlab (VBA toolbox, SPM), R (JAGS, BRMS)}\par
\gray{Project management: Behavioral study}\par
\gray{PIs: Marie Claire Villeval, Jean-Claude Dreher}

\vspace{0.9em}

\bluebf{PhD | Neuroeconomics (ISCMJ \& GATE)}\par
CNRS UMR 5229 \& CNRS UMR 2824, France\par
October 2018 -- December 2022 \,|\, Social decision making

\gray{Studies: Neurocognitive mechanisms underlying transmission of uncertain information in humans.}\par
\gray{Tools: Matlab (VBA toolbox, SPM), R (JAGS, BRMS)}\par
\gray{Project management: Behavioral and neuroimaging studies}\par
\gray{PhD directors: Marie Claire Villeval, Jean-Claude Dreher}

\vspace{0.9em}

\bluebf{Research Internship | Neuroeconomics lab. (ISCMJ)}\par
CNRS UMR 5229, France\par
February -- July 2018 \,|\, Decision making \& rewarding

\gray{Study: gPPI analysis of testosterone--induced effects on orbitofrontal-amygdala relationships during anticipation of primary and secondary rewards.}\par
\gray{Tools: Matlab (SPM, CONN)}\par
\gray{Missions: Brain functional connectivity analysis}\par
\gray{PI: Jean-Claude Dreher}

} % end page

% ============================================================
% PAGE 2
% ============================================================
\cvpage{

\lrule

\lsectionblock{SKILLS}{
\gray{Computational Modeling \& Simulation}\par
\gray{Bayesian Statistical Analysis \& Inference}\par
\gray{Reinforcement Learning \& Decision-Making Models}\par
\gray{Experimental Design \& Behavioral Task Optimization}\par
\gray{Project Leadership \& Cross-Disciplinary Collaboration}\par
\gray{Teaching, Mentoring \& Scientific Communication}
}

\lsectionblock{FELLOWSHIPS}{
\gray{LabEX CORTEX fellowship (2022--2023)}\par
\gray{LabEX CORTEX fellowship (2021--2022)}\par
\gray{IDEX INDEPTH PhD fellowship (2018--2021)}
}

\lsectionblock{CONTRIBUTIONS}{
\gray{Cortex-magazine, editorial board member}\par
\gray{(January 2023 -- January 2024)}
}

\lsectionblock{AFFILIATIONS}{
\gray{Affiliate, AI Interdisciplinary Institute at Maryland (2024--ongoing)}\par
\gray{Affiliate, Neuroscience and Cognitive Science (NACS) program (2025--ongoing)}
}



}{
\rheading{RESEARCH EXPERIENCE}

\bluebf{Research Internship | Neuroeconomics lab. (ISCMJ)}\par
CNRS UMR 5229, France\par
June -- August 2017 \,|\, Decision making \& rewarding

\gray{Studies: Functional connectivity analysis in rewarded tasks and implementation of moral norms in tDCS disrupted decision-making behaviors.}\par
\gray{Tools: Matlab (SPM, CONN)}\par
\gray{Missions: fMRI analysis; research and ethics protocols}\par
\gray{PI: Jean-Claude Dreher}

\vspace{0.9em}

\bluebf{Additional early experiences (summary)}\par
\gray{Integrative and Adaptative Neurosciences Laboratory (CNRS UMR 7260, 2016): vestibular cortex; complex systems modelling.}\par
\vspace{0.7em}
\gray{Cognitive Psychology Laboratory (CNRS UMR 7290, 2015); La Poste: nudging risky behaviors and ecological transition.}\par
\vspace{0.7em}
\gray{Speech and Language Laboratory (CNRS UMR 7309, 2014): theory of mind; schizophrenia; data collection and behavioral analysis.}

\vspace{0.9em}



\rheading{TEACHING EXPERIENCE}

{\fontsize{10}{12}\selectfont

\bluebf{Teacher | NACS 645 Cognitive Science (U. of Maryland)}\par
\black{September--December 2025 \,|\, 11 PhD students}\par
\black{Content: }
\blackulink{https://valentinguigon.github.io/teaching/\#2025-umd}
{Foundational debates in cognitive science.}\par
\gray{Classes: Concepts; Modularity; Embodied cognition; Brain architecture; Cognitive architecture; Innateness; Methods; Social cognition; Intercultural cognition; Cognitive systems; Thinking; NeuroAI.}\par
\vspace{0.7em}

\bluebf{Teacher | Cortecs Critical Thinking Summer School (France)}\par
\black{July 2025 \,|\, 20 students}\par
\black{Content: }
\blackulink{https://valentinguigon.github.io/teaching/2025_Cortecs_Cours_entier/}
{Information; Beliefs; Predictions.}\par
\vspace{0.7em}

\bluebf{Mentor | UMD PhD (U. of Maryland)}\par
\black{September 2024--April 2025 \,|\, 1 student}\par
\vspace{0.7em}

\bluebf{Mentor | Neurosciences Master 1 (U. Claude Bernard Lyon 1)}\par
\black{January--June 2023, 2024 \,|\, 2 $\times$ 3 students}\par
\vspace{0.7em}

\bluebf{Teacher | SPM fMRI preprocessing \& contrasts (U. Claude Bernard Lyon 1)}\par
\black{June 2023 \,|\, 20 PhD students}\par
\black{Content: }
\blackulink{https://valentinguigon.github.io/teaching/2023_NSCO_fMRI_course/}
{fMRI preprocessing and first-level modeling with SPM.}\par
\vspace{0.7em}

\bluebf{Teaching assistant | Cognitive Psychology (U. Lumière Lyon 2)}\par
\black{September--December 2018, 2019, 2020 \,|\, 4 $\times$ 40 students}\par
\gray{Course: Cognitive psychology, Licence 2}\par
\gray{Classes: Research methodology; Emotions; Working memory; Executive functions; Language.}\par
\gray{Supervisor: Gaën Plancher.}\par
\vspace{0.7em}

\bluebf{Teaching assistant | Intro. to cognitive psychology (U. Lumière Lyon 2)}\par
\black{September--December 2017 \,|\, 2 $\times$ 40 students}\par
\gray{Course: Introduction to cognitive psychology, Licence 1}\par
\gray{Classes: Research methodology; Theoretical and experimental paradigms.}\par
\gray{Supervisor: François Osiurak.}\par

} % end fontsize scope

} % end page

% ============================================================
% PAGE 3
% ============================================================
\cvpage{

\lrule

\lsectionblock{EXTERNAL\\TRAINING}{
\raggedright

\yearhdr{2025}
\trainitem{Hugging Face AI Agents, 28h}{}

\yearhdr{2024}
\trainitem{Hugging Face Deep RL, 28h}{Certified}
\trainitem{Reproducible Research, INRIA (FUN-MOOC), 24h}{Certified}
\trainitem{ML with scikit-learn, INRIA (FUN-MOOC), 36h}{Certified}
\trainitem{Structural Equation Modeling, CenterStat, 18h}{Certified}
\trainitem{Game Theory, Stanford U. (Coursera), 17h}{}

\yearhdr{2023}
\trainitem{Hugging Face NLP Course, 49h}{}
\trainitem{CS50, Harvard U. (edX), 30h}{}
\trainitem{ML with Python, IBM (Coursera), 15h}{}

\yearhdr{2022}
\trainitem{Bayesian Statistics in Evolutionary Biology, LBBE, UCBL1, 27h}{Certified}

\yearhdr{2021}
\trainitem{Statistical Bayesian Modelling, L. Nalborczyk, MaiMoSiNe, 20h}{Certified}
\trainitem{Integrity and Ethics in Research Careers, UDL (FUN-MOOC), 30h}{Certified}

\yearhdr{2020}
\trainitem{Model Thinking, S.E. Page (Coursera), 27h}{}

\yearhdr{2019}
\trainitem{Noninvasive Brain Stimulation Workshop, 14h}{Certified}
\trainitem{Leaders of Learning, Harvard U. (FUN-MOOC), 15h}{Certified}
\trainitem{Intro. to Neuroeconomics (Coursera), 31h}{}

\yearhdr{2018}
\trainitem{Principles of fMRI I \& II, M. Lindquist (Coursera), 17h}{}

}



}{
\rheading{PUBLICATIONS}

\parbox{0.95\linewidth}{\centering
\blackbf{Guigon, V.}\black{, Geay, L., \& Charpentier, C. J. (2026). }
{Rethinking misinformation through plausibility estimation and confidence calibration. }
\black{\textit{Communications Psychology}, in press.}\par
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\blackbf{Guigon, V.}\black{, Villeval, M. C., \& Dreher, J. C. (2024). }
\blackulink{https://www.nature.com/articles/s44271-024-00170-w}
{Metacognition biases information seeking in assessing ambiguous news. }
\black{\textit{Communications Psychology}, 2(1), 122.}\par
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\black{Hu, Y.,} \blackbf{Guigon, V.}\black{, Philippe, R., Zhao, S., Derrington, E., Corgnet, B., \ldots{} \& Dreher, J. C. (2022). }
\blackulink{https://journals.sagepub.com/doi/abs/10.1177/09567976211042379}
{Perturbation of Right Dorsolateral Prefrontal Cortex Makes Power Holders Less Resistant to Tempting Bribes. }
\black{\textit{Psychological Science}, 33(3), 412--423.}\par
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\black{O'Connor, D. A., Janet, R., }\blackbf{Guigon, V.}\black{, Belle, A., Vincent, B. T., Bromberg, U., \ldots{} \& Dreher, J. C. (2021). }
\blackulink{https://www.cell.com/iscience/fulltext/S2589-0042(21)00260-1}
{Rewards that are near increase impulsive action. }
\black{\textit{iScience}, 24(4), 102292.}\par
}

\vspace{0.9em}



\rheading{MANUSCRIPTS IN PREPARATION}

\parbox{0.95\linewidth}{\centering
\blackbf{Guigon, V.}\black{, Topel, S., Charpentier, C. J. Individual differences in dynamic belief updating during trust learning.}\par
{\small\emph{\blackulink{https://valentinguigon.github.io/assets/pdf/posters/Poster_2025_SNE_CISE.pdf}{Conference presentations}: SNE (2025); CISE (2025).}}
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\blackbf{Guigon, V.}\black{, Benistant, J., Villeval, M. C., Dreher, J.-C. Neurocomputational processes of inferring others’ preferences for information .}\par
{\small\emph{\blackulink{https://valentinguigon.github.io/assets/pdf/posters/Poster_2023_SBDM_A0.pdf}{Conference presentations}: SBDM (2021, 2023); SNE (2021).}}
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\blackbf{Guigon, V.}\black{, Dunne, S., Pazderska, A., Frodl, T., Nolan, J. J., Clairis, N., O’Doherty, J. P., Dreher, J.-C. Testosterone causes decoupling of orbitofrontal cortex--amygdala relationship while anticipating primary and secondary rewards.}\par
{\small\emph{\blackulink{https://valentinguigon.github.io/assets/pdf/posters/Poster_2018_ofcmeeting_A0.pdf}{Conference presentation}: OFC Meeting (2018).}}
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\black{Benistant, J., }\blackbf{Guigon, V.}\black{, Nicolas, A., Derrington, E., \& Dreher, J. C. (2025). } 
\blackulink{https://www.biorxiv.org/content/10.1101/2024.05.21.594859v1.abstract}
{Dynamic valuation bias explains social influence on cheating behavior. }
\black{\textit{bioRxiv}.}\par}
\vspace{0.7em}

\vspace{0.9em}

\rheading{SCIENCE DISSEMINATION}

\parbox{0.95\linewidth}{\centering
\gray{Valentin Guigon }
\grayulink{https://valentinguigon.substack.com/}{Substack}\par
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\gray{Valentin Guigon }
\grayulink{https://medium.com/@valentin.guigon}{Medium}\par
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\graybf{V. Guigon (2025). }
\grayulink{https://cortecs.org/informations-medias/la-sphere-publique-et-la-chambre-decho/}
{La sphère publique et la chambre d’écho. }
\gray{Cortecs.org.}\par
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\gray{S. Tremblay \& CheeseNaan Productions (2024). }
\grayulink{https://open.spotify.com/episode/60KNvDzRGybcj7CtiYglTi?si=93b89657cbf64983}
{Au-delà des écrans : comprendre la désinformation en ligne.}\par
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\graybf{V. Guigon (2023). }
\grayulink{https://www.cortex-mag.net/notre-societe-est-elle-de-plus-en-plus-polarisee/}
{Notre société est-elle de plus en plus polarisée ? }
\gray{Cortex-mag.net.}\par
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\gray{A. Sorce (2021). }
\grayulink{https://pharefm.com/2021/09/10/linvite-de-la-semaine-valentin-guigon-fake-news-complot/}
{L’invité de la semaine – Valentin Guigon, fake news et théories du complot. }
\gray{Pharefm.com.}\par
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\gray{O. Mollaret (2021). }
\grayulink{https://www.rue89lyon.fr/2021/08/16/lyon-victimes-fake-news/}
{À Lyon : les victimes de fake news « fonctionnent comme tout le monde ». }
\gray{Rue89lyon.fr.}\par
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\gray{Yanis (2021). }
\grayulink{https://smartlink.ausha.co/cognitif/episode-bonus-comment-ne-pas-se-faire-avoir-par-les-fake-news}
{Comment ne pas se faire avoir par les fake news ? }
\gray{Alveole.media / Cognitif.}\par
}
\vspace{0.7em}

\parbox{0.95\linewidth}{\centering
\gray{A. Gabert (2020). }
\grayulink{https://www.cortex-mag.net/pourquoi-les-theories-du-complot-plaisent-a-notre-cerveau/}
{Pourquoi les théories du complot plaisent à notre cerveau. }
\gray{Cortex-mag.net.}\par
}


\vspace{0.9em}

} % end page
\end{document}
